Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-30 documentation/paper.tex
Updated graphs with enforced range of 0 to 1

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{banded_no_pos_input_hist}
    \caption{\label{banded_no_pos_input_hist} Prediction distribution of the best {\it FourierMLP}$(PosCor(\beta_{8}))$ discriminator.}
\end{figure}

Table \ref{fft_wall_cuts} compares various multi-layer perceptron discriminators from the most effective region of the hyperparameter search space (L2 $\lambda$ of 0.003 for $\beta_8$ input, and L2 $\lambda$ of 0.001 and dropout of 0 for $\beta_{50,001}$ input). It is very clear that higher resolution data does not improve accuracy in a relatively shallow network.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{banded_no_pos_input_hist}
    \caption{\label{banded_no_pos_input_hist} Prediction distribution of the best {\it FourierMLP}$(${\it PosCor}$(\beta_{8}))$ configuration.}
\end{figure}

Table \ref{fft_wall_cuts} compares various multi-layer perceptron discriminators from the most effective region of the hyperparameter search space (L2 $\lambda$ of 0.003 and 2 layers for $\beta_8$ input, and L2 $\lambda$ of 0.001 and dropout of 0 for $\beta_{50,001}$ input). It is very clear that higher resolution data does not improve accuracy in a relatively shallow network.
